Identification and Spatial Analysis of Law Firms Naming Patterns in Russia Using Text Embeddings

### 2025-01-27 law-firms-names/Paper.Rmd
Revert from umap-dbscan to kmeans, reassign strategies and categories, switch from clusters to categories, make a dendrogram of categories with strategies and a map of localmoran i, make other changes, delete useless code from script, #4

---
title: "Identification and Spatial Analysis of Russian Law Firms Naming Patterns Using Text Embeddings"
author: "Pavel Syomin"
output:
  word_document:
    reference_doc: "journal-article/reference.docx"
bibliography: "journal-article/refs.bib"
csl: "journal-article/apa.csl"
link-bibliography: False  
---

@@

Law firm names may follow a number of patterns. A pattern can be defined as as a typical model, or pattern, of brand construction identified by usage of identical or semantically similar words or phrases. For example, names with the words “law firm” or “law company” follow one pattern, and names with the words “legal aid” are an example of another pattern. Patterns may be grouped multiple times forming a tree-like classification [@Anora2015].

It seems reasonable to posit that (1) several law firms naming strategies may be identified in Russia and (2) there is a spatial heterogeneity in the distribution of the firms with different naming strategies. Law firms naming strategy here is defined . The potential viability of these two statements cannot be directly conducted from the existing research, but it relies on a common-sense observations about the similarities and differences of law firm names in and between various regions of the country. Law firm names are likely to reflect some economic and, to a lesser extent, cultural characteristics of the territories where these firms are located. Thus, given the vast area and a material heterogeneity of economical and cultural landscape of Russia, these names should not have a uniform spatial distribution either. The primary objective of this paper is to discover these hypothesized naming strategies and their spatial heterogeneity (if any). In addition, it aims to test whether the variation of law firms naming between settlements in Russia is contingent upon the geographical proximity of settlements and economic links between them. Building upon the Tobler's First Law of Geography (“near things are more related than distant things”) [@Tobler1970], it can be hypothesized that both these factors have a positive impact on the similarity of law firm names, because small geographic distance directly makes settlements “near”, as well as economic links make them to be “near” in economical meaning. Finally, due to quite a pilot nature of this paper, it also tries to handle all intriguing side observations about the law firms naming strategies and their spatial distribution in Russia that may arise from the exploratory analysis of the data, even if no robust testing can be performed.

@@

The downloadable version of the registry includes, in particular, firm names, addresses of registration (up to a settlement), and codes of activity kinds compatible with NACE Rev.2. It should be noted that the registry does not include several types of firms, e.g. foreign commercial law firms without a juridical person registered according to Russian law, non-profit organizations, bar (advocacy) establishments, large companies etc. This results in some data being absent. Nevertheless, this issue should be considered insignificant for a variety of reasons. Foreign law firms usually register their affiliated juridical person in Russia and thus are not omitted in the registry. Non-profit organisations' share on Russian legal market does not exceed 1% [@Moiseeva2016]. The names of bar establishments are usually quite uniform, containing the kind of the establishment (cabinet of an advocate, bureau of advocates, college of advocates, juridical consultancy) accompanied with a personal name(s) of advocates or with a mention of geographical location of a particular establishment, thus their potential spatial heterogeneity is not characteristic. A matching of the list of the law firms obtained from the SME registry with the extract of law firms from the Russian Financial Statements Database shows that ~3,300 of the firms present in SME registry in 2023 are absent from RFSD, and ~5,200 firms present in RFSD are missing in SME registry. The balance of missing records is not that far from the equality, and with the total number of law firms in SME registry (~34000) the share of missing entries is below 15%. Consequently, the completeness of information is relatively high, and it can be used to draw reliable conclusions.

@@

The data used in the study covers a period of six years, from 2016 to 2021. The initial point in time is defined by the commencement of SME registry data availability. The finish point, 2021, is the latest year, is the latest year with “normal” conditions in Russia not impacted by military operation in Ukraine and consequent international sanctions and domestic economic and political perturbations. The purpose of temporal dimension is to exclude short-living law firms that are likely to be dummy companies. Organizations with a lifespan of less than three years have been omitted from the research, while all the remaining have been included in the further analysis.

@@

The autocorrelation analysis has two branches differing in the way the spatial weights matrix is constructed. In the first branch, neighborhood of the regions is defined based on the adjacency of region's polygons. Sakhalin and Kaliningrad regions, being enclaves and thus having zero immediate neighbors, were manually connected with a few closest regions. In the second branch, the neighborhood of the regions was identified based on their belonging to the same economic region according to the classification widely used by economic geographers and spatial development practitioners in Russia for decades and outlined, for example, in [@Leyzerovich2010]. All regions within the same economic region are considered to be connected, and all regions of the different economic regions are disconnected, resulting in spatial weights graph comprised of several independent components. Despite the fact that the concept of economic regions in Russia is sometimes considered legacy, it is still implicitly used by researchers and practitioners, and the belonging to the same economic regions implies economic linkage, similarity and cooperation of regions. Thus, it makes sense to utilize this classification.

@@

>>>>

---
title: "Identification and Spatial Analysis of Law Firms Naming Patterns in Russia Using Text Embeddings"
author: "Pavel Syomin"
output:
  word_document:
    reference_doc: "journal-article/reference.docx"
bibliography: "journal-article/refs.bib"
csl: "journal-article/apa.csl"
link-bibliography: False  
---

@@

Law firm names may follow a number of patterns. A pattern can be defined as as a typical model, or pattern, of brand construction identified by usage of identical or semantically similar words or phrases. For example, names with the words “law firm” or “law company” follow one pattern, and names with the words “legal aid” are an example of another pattern. Patterns may be grouped multiple times forming a tree-like classification [@Anora2015]. Such classification may become a basis for identifying naming strategies. Compared to naming patterns, naming strategies are broader groups of firm names that are usually based on sharing a common purpose — e.g. emphasis the belonging of a company to a certain activity type. @BassolsiGardella2023 argue for a two-dimensional Strategic Naming Model (SNM) that includes two pairs of strategies: belonging and uniqueness, no-strategy and market. Pairs may be represented as X and Y axes of a plot, respectively, with paired strategies taking opposite positions on these axes: belonging is an opponent of uniqueness, market is an opponent for no-strategy. Authors of the aforementioned paper discover a difference in naming strategies composition of tourist industry firms in three Columbia cities. Probably such a variation is not be limited to Columbia cities and tourism and can be found in the case with law firms in Russia.

The aim of this research is twofold. First, it tries to identify law firms naming patterns in Russia and categorize them following the framework of SNM. Second, it seeks to check whether there are regularities in the spatial distribution of law firms naming patterns. The potential viability of these two statements cannot be directly conducted from the existing research, but it relies on a common-sense observations about the similarities and differences of law firm names in and between various regions of the country. According to the famous Tobler's First Law of Geography, “near things are more related than distant things” [@Tobler1970], so there is a chance that law firms naming patterns may form spatial clusters and hotspots that at least a bit reflect some economic and, to a lesser extent, cultural similarities of the territories where these firms are located. Given the vast area and a material heterogeneity of economical and cultural landscape of Russia, these names should not have a uniform spatial distribution. However, it is just a hypothesis that needs testing.

@@

The downloadable version of the registry includes, in particular, firm names, addresses of registration (up to a settlement), and codes of activity kinds compatible with NACE Rev.2. It should be noted that the registry does not include several types of firms, e.g. foreign commercial law firms without a juridical person registered according to Russian law, non-profit organizations, bar (advocacy) establishments, large companies etc. This results in some data being absent. Nevertheless, this issue should be considered insignificant for a variety of reasons. Foreign law firms usually register their affiliated juridical person in Russia and thus are not omitted in the registry. Non-profit organisations' share on Russian legal market does not exceed 1% [@Moiseeva2016]. The names of bar establishments are usually quite uniform, containing the kind of the establishment (cabinet of an advocate, bureau of advocates, college of advocates, juridical consultancy) accompanied with a personal name(s) of advocates or with a mention of geographical location of a particular establishment, thus their potential spatial heterogeneity is not characteristic. A matching of the list of the law firms obtained from the SME registry and active in 2023 with the extract of law firms from the Russian Financial Statements Database for the same year shows that ~3,300 of the firms present in SME registry are absent from RFSD, and ~5,200 firms present in RFSD are missing in SME registry. The balance of missing records is not that far from the equality, and with the total number of law firms in SME registry (~34000) the share of missing entries is below 15%. Consequently, the completeness of information is relatively high, and it can be used to draw reliable conclusions.

@@

The data used in the study covers a period of six years, from 2016 to 2021. The initial point in time is defined by the commencement of SME registry data availability. The finish point, 2021, is the latest year, is the latest year with “normal” conditions in Russia not impacted by military operation in Ukraine and consequent international sanctions and domestic economic and political perturbations. The purpose of temporal dimension is to exclude short-living law firms that are likely to be dummy companies. Organizations with a lifespan of less than three years have been omitted from the research, while all the remaining have been included in the further analysis. In addition, the utilization of multi-year data acts as a form of averaging, smoothing the potential distortions of spatial structure resulting from the random year-to-year changes of active law firms list.

@@

Six spatial weights matrices are used to ensure the robustness of the results. Three of these matrices are constructed with K nearest neighbours technique based on the location of region's centroids, where K equals 3, 4 or 6, respectively. Another matrix also uses geographical properties of regions, but instead of centroids, it relies on the existence of common border lines or points to identify neighbouring regions. Sakhalin and Kaliningrad regions, being enclaves and thus having zero immediate neighbors, were manually connected with a few closest regions. Two remaining matrices treat regions belonging to the same upper-level metaregion as neighbours, and all the other regions as non-neighbours. For one of these two matrices, economic regions act as metaregions, and for another, federal districts are used in this fashion. Economic regions are defined according to the classification widely used by economic geographers and spatial development practitioners in Russia for decades and outlined, for example, in [@Leyzerovich2010]. Federal districts composition is defined in the Executive Order of the President of Russia No. 849, Dated May 13, 2000, “On the Plenipotentiary Representative of the President of the Russian Federation in the Federal District” (with up-to-date amendments).

@@

### 2.2.6. Data statistics

There are `r initial_firms_count` law firms in the SMB registry in the selected period with `r nrow(unique_names)` unique firm names. From the initial dataset, `r valid_firms_count` law firms have existed for at least three years and have been selected for the analysis. Their names sometimes are duplicated, and the number of unique law firm names being analysed is `r`.
